---
title: "Anecdotal Evidence Story Map"
author: "Katie MacIntosh"
date: "November 29, 2016"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries, message=FALSE, error=FALSE}

library(tidyverse)
library(ggmap)
library(leaflet)
library(htmlwidgets)
```

# Import data

The "ae_storymap" .csv file was constructed manually by listening to the story recordings. Some stories were very specific and provided a point location, i.e. "Van Dusen Botanical Garden", while others only referred to a broad geographic area, like "France", for example. I separated these into different columns based on scale, ie. "location", "city", "country", etc. By concatenating the locations in these columns, I ended up with one location to be geocoded.

For geocoding, I used the 'geocode' function in the ggmap package.

```{r data, message = FALSE}
storymap_df <- read_csv("data/ae_storymap.csv") %>%
  mutate(to_geocode = paste((coalesce(location, "")), 
                            (coalesce(city, "")), 
                            (coalesce(state_province, "")), 
                            (coalesce(country, "")), sep = " "))
# geocode
storymap_geocoded <- storymap_df %>% 
  as.data.frame() %>% 
  mutate_geocode(to_geocode)
```

# Generate popups

This constructs the HTML for the popup, which includes the speaker's name and bio, a link to the corresponding post on the Anecdotal Evidence page, and the embedded .mp3 of their story.

```{r popup}
# template for blog link
blog_link <- paste0("<h3><a href='%s' style='text-decoration:none'>",
                    "%s</a></h3>")
# template for audio player
player <- paste0("<audio controls style='width:100%%'>",
                 "<source src='%s' type='audio/mpeg'></audio>")
storymap_popup <- storymap_geocoded %>% 
  # generate html for popup
  mutate(popup_html = paste0(sprintf(blog_link, link, storyteller),
                             "<p>", description, "</p>",
                             sprintf(player, audio_file)))
```

# Leaflet

```{r map create}

m <- leaflet(storymap_popup) %>% 
  addProviderTiles("OpenStreetMap.BlackAndWhite") %>% 
  addCircleMarkers(lng = ~lon, lat = ~lat, radius = 8, 
                   stroke = TRUE, color = '#aaa', weight = 1, 
                   fillColor = '#69d2e7', fillOpacity = 0.8,
                   popup = ~popup_html,
                   clusterOptions = markerClusterOptions(showCoverageOnHover = FALSE,
                                                         zoomToBoundsOnClick = TRUE,
                                                         iconCreateFunction=JS("function (cluster) {            var childCount = cluster.getChildCount();  
                if (childCount < 100) {  
                  c = 'rgba(45, 132, 200, 1.0);'
                } else { 
                  c = 'rgba(241, 128, 23, 1);'  
                }    
        return new L.DivIcon({ html: '<div style=\"background-color:'+c+'\"><span>' + childCount + '</span></div>', className: 'marker-cluster', iconSize: new L.Point(40, 40) });

  }")))



m


```

# Full screen

Create a stand alone HTML file of the [full screen map](ae-storymap.html).

```{r full-screen}
saveWidget(m, file = 'ae-storymap.html', selfcontained = TRUE)
```
```
